---
title: "Untitled"
author: "Yang Zhang"
date: "8/29/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
library(yzmiscf)
library(dplyr)
library(ggplot2)
```

step 1: read in raw pcr table
step 2: grep variable
step 3: de-replication
step 4: calculate fold change
step 5: export as a new table
step 6: make a plot.

```{r}
raw <- read.csv("/Users/yangzhang/Desktop/test.csv")
## de-duplication(replication)
varrr <- raw %>%
  select(id, variable) %>%
  distinct(id, .keep_all = TRUE)

clean <- raw %>%
  group_by(id) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  mutate(treatment = varrr$variable)

## calculate fold change using delta delta ct method
control <- clean %>%
  filter(treatment == "hfd")

dct_ctr = mean(control$gene1_ct) - mean(control$ref_ct)


expression <- clean %>%
  mutate(dct = gene1_ct - ref_ct) %>%
  mutate(ddct = dct - dct_ctr) %>%
  mutate(fold = 2^(-ddct))

ggplot(expression, aes(x = treatment, y = fold, fill = treatment)) +
  geom_boxplot() +
  geom_jitter(width = 0.15)
```


```{r}
#path = here("scratch")
liver_raw <- read.csv("/Users/yangzhang/Box/yzmiscf/scratch/liver.csv")

vars <- liver_raw %>%
  select(id, variable) %>%
  distinct(id, .keep_all = TRUE)

clean <- liver_raw %>%
  group_by(id) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  mutate(treatment = vars$variable) %>%
  select(id, treatment, everything()) ## sort, put variables up front

col_names <- names(clean)[3:ncol(clean)]

control <- clean %>%
  filter(treatment == "HFD")



dCt <- dct_ctr(control)
```
#' @title A Miscellaneous Function
#'
#' @description This function allows you to take PCR raw data, clean it, calculate fold change, then export as a new table.
#' @param genes Defaults.
#' @keywords PCR
#' @export
#' @examples
#' summ_stat()
raw2 <- readCtData(files = "/Users/yangzhang/Desktop/YZ2861.txt", format = "CFX", n.features = 96)
anova_sum <- function(genes, n) # n = row number
{
  output <- data.frame(matrix(ncol = 2, nrow = n))
  x <- c("gene", "anova pvalue")
  colnames(output) <- x
  varnames = c(colnames(genes[3:42]))
  list_fit <- list()
  list_2 <- list()
  for(i in 3:ncol(genes))
  {
    list_fit[[i]] <- aov(unlist(genes[i]) ~ unlist(genes[2]))
    list_2[[i]] <- summary(list_fit[[i]])[[1]]$`Pr(>F)`[[1]]
  }
  output[,1] <- varnames
  output[,2] <- unlist(list_2[3:42])
  output
}
control <- clean %>%
  filter(treatment == "HFD")

col_names <- names(clean)[4:ncol(clean)]



#'
liver_raw <- read.csv("/Users/yangzhang/Box/yzmiscf/scratch/liver.csv")
clean <- cleanme(liver_raw)


plot.foldch <- function(expression){
  ggplot(expression,
         aes(x = treatment, y = col_name,
             fill = treatment)) +
    geom_boxplot() +
    geom_jitter(width = 0.12)
}
